Abstract Data Type Inference

### 2015-03-11 inference.tex
Segue between refinement and inference.

In order to frame the symbolic ADT inference problem, we fix a natural symbolic
representation of ADTs. A \emph{history formula} $F$ is a first-order logic
formula with
\begin{itemize}

>>>>

Recent works demonstrate efficient algorithms\footnote{In time polynomial in
the number of operations, per execution.} for checking observational
refinement~\cite{conf/popl/BouajjaniEEH15, conf/pldi/EmmiEH15}, yet rely on
hand-written symbolic ADT representations. In order to frame the problem of
computing these automatically, we fix a language for symbolic representation. A
\emph{history formula} $F$ is a first-order logic formula with
\begin{itemize}
